\documentclass[12pt]{article}
\usepackage{amsmath,amssymb,amsthm,amsfonts}
\usepackage{multicol}
\usepackage{color}
\usepackage{hyperref}
\usepackage{graphicx}

\newcommand{\co}[1]{\stackrel{\circ }{#1}}
\newcommand{\gf}{\mathfrak{g}}
\newcommand{\nfp}{\mathfrak{n}^{+}}
\newcommand{\nfm}{\mathfrak{n}^{-}}
\newcommand{\af}{\mathfrak{a}}
\newcommand{\uf}{\mathfrak{u}}
\newcommand{\sfr}{\mathfrak{s}}
\newcommand{\aft}{\widetilde{\mathfrak{a}}}
\newcommand{\afb}{\mathfrak{a}_{\bot}}
\newcommand{\hf}{\mathfrak{h}}
\newcommand{\hfb}{\mathfrak{h}_{\bot}}
\newcommand{\pf}{\mathfrak{p}}

\newcommand{\gfh}{\hat{\mathfrak{g}}}
\newcommand{\afh}{\hat{\mathfrak{a}}}
\newcommand{\sfh}{\hat{\mathfrak{s}}}
\newcommand{\bff}{\mathfrak{b}}
\newcommand{\hfg}{\hf_{\gf}}

\begin{document}
\title{Schramm-Loewner evolution martingale equation and Cardy conditions in Wess-Zumino-Novikov-Witten models}

\maketitle

\begin{abstract}
  We can write martingale condition with respect to Schramm-Loewner evolution as an equation on
  boundary condition changing operator. This equation has discrete set of solutions, so we have a
  classification of boundary conditions producing SLE traces. On the other hand Cardy conditions
  provide full classification of conformally-invariant boundary conditions. We describe the
  intersection and difference of these two sets of solutions. 
\end{abstract}

Heroes: SLE with random gauge transforms, WZNW-model, classification of Cardy conditions solutions. 

Story: WZNW-model connects parameters of SLE and random gauge transform, martingale condition leads
to classification of solutions. This classification is compared with Cardy conditions. 

Consider Scharmm-Loewner evolution with additional random walk on simple Lie group $G$. It is a
stochastic process $(w_{t}, \Omega_{t}(z))$ in $\mathbb{C}\times G$ satisfying stochastic
differential equations $d w_{t}(z)=\frac{dt}{w_{t}(z)}-\sqrt{\kappa} d\xi_{t}$, $d \Omega_{t}(z) =
\frac{\sum_{a} t^{a} d\theta^{a}}{z-z_{0}}$

Consider Wess-Zumino-Novikov-Witten model on the upper half-plane.


 Correlation function of the form
$\left<\phi(0) \varphi_{1}(w_{1})\dots \varphi_{n}(w_{n}) \phi^{*}(\infty)\right>$ that is
martingale with to the stochastic process $(w_{t}(z), \Omega_{t}(z))$ $d w_{t}(z)=\frac{dt}{w_{t}(z)}-\sqrt{\kappa} d\xi_{t}$ if
and only if the state $L_{-2}+\frac{\kappa}{2} L_{-1}^{2} +\frac{\tau}{2}$

\end{document}
